Common sense approaches to sharing tabular data alongside publication

### 2021-09-18 new-paper.Rmd
Fixed two typos

Journals provide data papers in a formal publication explaining data that is archived (e.g. Ecology, Scientific Data). This is a familiar avenue for researchers to receive credit and citation. Writing a data paper can be very useful for researchers, but, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing. We recommend partnering with best practice data repositories that emphasize curation, like Dryad. This way the data will have a long-term archiving and will also have professional curation to ensure that the published data are usable and have enough metadata to be understood. While writing a data paper can be very useful for researchers, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing. Data journals should routinely be partnering with best practice repositories to best support the underlying data.

@@

When citing data, you should cite the preferred CITATION file in the first instance, else, a data publication, (for example in _Scientific Data, Ecology_), and if none of those apply, cite the repository in which the data is deposited (e.g., a Zenodo repository).

>>>>

Journals provide data papers in a formal publication explaining data that is archived (e.g. Ecology, Scientific Data). This is a familiar avenue for researchers to receive credit and citation. Writing a data paper can be very useful for researchers, but, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing. We recommend partnering with best practice data repositories that emphasize curation, like Dryad. This way the data will have long-term archiving and will also have professional curation to ensure that the published data are usable and have enough metadata to be understood. While writing a data paper can be very useful for researchers, journals that publish data papers lack guidelines on how to structure data for effective reuse and sharing. Data journals should routinely be partnering with best practice repositories to best support the underlying data.

@@

When citing data, you should cite the preferred CITATION file in the first instance, else, a data publication, (for example in _Scientific Data, Ecology_), and if none of those apply, cite the repository in which the data is deposited (e.g., a Zenodo repository) in the references section of related papers.
